Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-15 paper.tex
edit in conclusions

\revise{The new formulation for \texttt{pyJac}, including both constant-volume and constant-pressure assumptions, resulted in highly sparse chemical kinetic Jacobians.
Though the Jacobian approximation discussed in~\cref{S:sparsity} is not a key feature of this work, future efforts to develop more sophisticated Jacobian approximations would be a worthwhile endeavor.}

>>>>

\revise{The new molar-concentration-based formulation for \texttt{pyJac} resulted in highly sparse chemical kinetic Jacobians,
and allows selection of either the constant-volume or constant-pressure approximation.
In addition, sparsity can be increased further by eliminating components associated with the bath gas, as discussed in \cref{S:sparsity};
this approximation is not a key feature of this work, and future efforts to develop more sophisticated Jacobian approximations based on the \texttt{pyJac} software would be a worthwhile endeavor.}
